A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-02-28 introduction.tex
Finally 23 pages
Define the problem

@@

Parikh image computations, as well as Parikh automata, feature extensively in
string solvers, including as mentioned above \Ostrich{} and \OstrichPlus{}
\cite{ostrich,ostrich-plus}, but also forms the basis of
\textsc{Trau}~\cite{trau-pldi},
and occurs in \textsc{Sloth}~\cite{sloth}. Parikh images frequently appear when
introducing cardinality constraints like length or string indexing. The
state-of-the-art approach to handling Parikh image computation is to
over-approximate the Parikh image of a product of $k$~automata
$\ParikhMap(\Language(\Automaton_1) \cap \ldots \cap \Language(\Automaton_k))$
with the conjunction of the automata's Parikh maps, $\bigwedge_{i=1}^{k}
\ParikhMap(\Automaton_i)$. Due to the over-approximation,
this approach works only for unsatisfiable instances,
and will require falling back to computing the product of the automata before
using the standard approach for finding its image originally presented
in~\cite{generate-parikh-image}.

>>>>

The most basic version fo the problem considered in this paper is:
{
    \centering
    \begin{tcolorbox}[colback=gray!5!white,colframe=gray!75!black,%
        title=Satisfiability of Parikh images of a product of automata,%
        width=0.8\linewidth]
        Given a finite set of regular languages, $\Language_1, \ldots, \Language_n$
        over a finite, common, alphabet $\Set{a_1, \ldots, a_k}$,
        and a Presburger formula, $\phi(\Vec{x_1, \ldots, x_k})$, 
        decide if there is a word, $w$ in the 
        intersection of $\Language_1, \ldots, \Language_n$, whose Parikh vector 
        $\Vec{m_1, \ldots, m_k}$ satisfies $\phi$.
    \end{tcolorbox}
  }

@@

Parikh image computations, as well as Parikh automata, feature extensively in
string solvers, including as mentioned above \Ostrich{} and \OstrichPlus{}
\cite{ostrich,ostrich-plus}, but also forms the basis of
\textsc{Trau}~\cite{trau-pldi},
and occurs in \textsc{Sloth}~\cite{sloth}. Parikh images frequently appear when
introducing cardinality constraints like length or string indexing. The
state-of-the-art approach to handling Parikh image computation is to
over-approximate the Parikh image of a product of $k$~automata
$\ParikhMap(\Language(\Automaton_1) \cap \ldots \cap \Language(\Automaton_k))$
with the conjunction of the automata's Parikh maps, $\bigwedge_{i=1}^{k}
\ParikhMap(\Language(\Automaton_i))$. Due to the over-approximation,
this approach works only for unsatisfiable instances,
and will require falling back to computing the product of the automata before
using the standard approach for finding its image originally presented
in~\cite{generate-parikh-image}.
